---
title: "Vehicles in the park"
output: 
  html_document: 
    code_folding: hide
    df_print: paged
    number_sections: yes
---

```{r setup, include=FALSE}
library(tidyverse)

scripts <- read_csv("scripts.csv")
all_existing_judgements <- read_csv("judgements.csv")

source("cj_functions.R")
```

# Judgement data

```{r}
all_existing_judgements %>% 
  group_by(study, judge_id) %>% 
  tally(name = "judgements_made_each") %>% 
  group_by(study, judgements_made_each) %>% 
  tally(name = "num_judges") %>% 
  relocate(num_judges, .before = judgements_made_each)
```


```{r}
# convert the slider scores to binary judgements
binary_judgements <- all_existing_judgements %>% 
  mutate(
    won = case_when(
      is.na(score) ~ won,
      score > 0 ~ right,
      score < 0 ~ left
    ),
    lost = case_when(
      is.na(score) ~ lost,
      score > 0 ~ left,
      score < 0 ~ right
    )
  ) %>% 
  # remove the attention checks
  filter(left != 0, right !=0) %>% 
  # remove the few cases where judges managed somehow to submit a slider score of 0
  filter(!is.na(won))
```

# Fit the Bradley-Terry model

```{r results='hide'}
btm_results <- binary_judgements %>% 
  # group the judgements by study and fit the BT model
  nest(csv_content = !c(study)) %>% 
  mutate(
    btm_stuff = map(csv_content, btm_for_cj, chosen_col = "won", notchosen_col = "lost", judge_col = "judge_id")
  ) %>% 
  unnest(cols = c(btm_stuff))
```

```{r}
btm_results %>% 
  select(-csv_content) %>% 
  mutate(ssr = as.numeric(ssr)) %>% 
  arrange(study)
```

## Item scores

The `btm_results` object includes `btm_estimates` giving the scores for each item. We write all these details out to `btm_estimates.csv`:

```{r}
btm_estimates <- btm_results %>% 
  select(study, btm_estimates) %>% 
  unnest(cols = c(btm_estimates)) %>% 
  select(-id) %>% 
  left_join(scripts %>% select(individual = item_num, word = item_name), by = "individual") %>% 
  relocate(word, .after = individual)

btm_estimates %>% 
  write_csv("btm_estimates.csv")

btm_estimates
```

Here is a visualisation of all the item scores in each study group, also saved to `btm_results.pdf`:

```{r fig.height=7, fig.width=10, warning=FALSE}
library(ggrepel)
theme_set(theme_minimal())

btm_estimates %>%
  left_join(btm_results %>% select(study, ssr, N_A), by = "study") %>% 
  mutate(panel_label = paste(" N = ", N_A, "\nSSR =", round(as.numeric(ssr), digits = 3))) %>% 
  group_by(study) %>% 
  arrange(theta) %>% 
  mutate(order = row_number()) %>% 
  ggplot(aes(x = order, y = theta, ymin = theta - se.theta, ymax = theta + se.theta)) +
  geom_hline(yintercept = 0, colour = "grey") +
  geom_pointrange(size = 0.25) +
  geom_text_repel(aes(label = word), box.padding = 0.3, min.segment.length = 0.5, colour = "#777777") +
  geom_text(
    mapping = aes(x = -Inf, y = Inf, label = panel_label),
    hjust   = -0.1,
    vjust   = 1
  ) +
  facet_grid(cols = vars(study), scales = "free") +
  theme(
    axis.text.x = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
  ) +
  labs(x = "")
ggsave("btm_results.pdf", units = "cm", width = 45, height = 25)
```

## Judge fits

A few judges have infit scores that are out of line with the majority of judges:

```{r}
judge_fits <- btm_results %>% 
  select(study, judge_fits) %>% 
  unnest(cols = c(judge_fits))

judge_fits %>% 
  ggplot(aes(y = infit, x = judgeName)) +
  geom_point(alpha = 0.1) +
  geom_text(aes(label = judgeName)) +
  facet_grid(cols = vars(study))

```
